---
title: "Simple document"
author: Lydia Parr  
date: 9/16/21
output: 
  github_document
---
#table of contents added with code abv, collapse code, can also do pdf 
#better not to do word because not editable 
#rmd is preferable for writng, use them for hw, can also do output for github

```{r}
library(tidyverse)
```


##knitting will print--- also knitting will show errors, so do it frequently
## because it creates new r session 

I'm an R Markdown document! (notice this part just looks like text

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:
(abvfromatting does bolding and italics respectively)
(below 3 backtics and a curly bracket for r code- it'll be in a chunk

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2
(you can put everything in the same place and it'll all work-- calculations
are included in the html file)
I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3 

Let's write a new code code (option+command+i instead of backticks for hotkeys)
(name code chunk, the text after r to help make troubleshooting easier)

options for code chunks to put in brackets after r {r}
eval = FALSE: code will be displayed but not executed; results are not included.
echo = FALSE: code will be executed but not displayed; results are included.
include = FALSE: code won’t be executed or displayed.
message = FALSE and warning = FALSE: prevents messages and warnings from being displayed.
results = hide and fig.show = hide: prevents results and figures from being shown, respectively.
collapse = TRUE: output will be collapsed into a single block at shown at the end of the chunk.
error: errors in code will stop rendering when FALSE; errors in code will be printed in the doc when TRUE. The default is FALSE and you should almost never change it.

This code chunk imports the 'tidyverse' package, creates a dataframe, and 
makes a histogram.


(could also load tidyverse in earlier code chunk and it'd be available early on
first code chunk ideally would load all packages/libraries you'll need to use)

```{r new_code_chunk}



##once files are in the same folder : create a new project, thing called project saves trouble
# use a folder on computer as an existing directory 

#also make sure what's inside tibble is reffed in 
#the line of code you save

plot_df = 
  tibble(
    x = rnorm(1000, sd = .5),
    y = 1 + 2 * x + rnorm(1000)
  )


plot_df = 
  tibble(
    x = rnorm(1000, sd = .5),
    y = 1 + 2 * x + rnorm(1000)
  )


plot_df ##kind of thing you can just put in console 

ggplot(plot_df, aes(x = x)) + geom_histogram()
##abv, made plot, told it x goes on x axis 
# ggplot was told to only look inside the plot 
#dataframe for the variables
## below, scatter not histo, x goes on x y goes on y

```

not everything will go into console-- run chunks individually by highlighting
and executing in console as if using an r script

Learning assessment 
```{r learning}

?rnorm##(to check what it does)
#remember to google and use the r search function
#okay to copu and paste if you understand what you're doing too 

#Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. 

library(tidyverse)
set.seed(12)

learning_df = 
  tibble(
    sample = rnorm(500, mean = 1),
    gr_than_0 = sample > 0,
    abs_val = abs(sample)
  )

ggplot(learning_df, aes(x = abs_val)) + geom_histogram()
```
ormatting text
There are a huge number of ways to format your documents. The overview below is essentially copied from R for Data Science; a link to a handy cheatsheet is below.

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell
